Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-24 paper/paper.tex
pass on section iv

\Mar{-------------------------- I am here}

\tname{} uses a composition of heuristic functions to sort the rules
produced in the previous step. Each of these functions uses a
different criterion to estimate how similar a created rule is to those
from public rulesets~\cite{emerging-threats-open}. The intuition is
that rules that look more similar to existing trusted rules are more
likely to be useful. The aggregated score of a rule is the weighted
average across the values produced by each heuristic function. The
co-domain of each function ranges on the 0-1 interval. Hence, the score
of a rule also ranges on the 0-1 interval. We describe in the
following each of these heuristic functions.

@@

\subsubsection{\label{sec:popularity-options}Popularity of options.}
One heuristic function that \tname{} uses to measure similarity
between a synthesized rule and a human-created rule is the popularity
of the options used in those rules. According to this heuristic, rules
containing popular options score higher compared to those containing
unpopular rules. Figure~\ref{fig:distribution-options} shows the
histogram of rule options for the ruleset we
used~\cite{emerging-threats-open}. The x-axis shows the options used
in rules (the 10 most common) and the y-axis shows the number of rules
using the corresponding option. Note that the options
\CodeIn{content}, \CodeIn{flow}, and \CodeIn{prce} are very
popular. \tname\ uses the following formula to compute the
contribution of option popularity to the score of a rule $r$:

{\small
\vspace{-2ex}
\[\sum_{i=1}^{N}\frac{\mathit{option\_frequency[option_i]}}{\mathit{max(option\_frequency)}}/N\]
\vspace{-2ex}
}

\noindent
The term $\mathit{option_i}$ denotes the $i$th option in the bitvector
encoding $r$. The term $\mathit{option\_frequency}$ encodes the
distribution of option popularity as a dictionary mapping
numbers---indicating popularity---to corresponding
options. Consequently, the term $\mathit{option\_frequency[option_i]}$
denotes the number of rules, from our dataset, containing
$\mathit{option\_i}$. The term $\mathit{max(option\_frequency)}$
refers to the maximum number of rules for any dictionary entry (to
normalize the measurement in the 0-1 range), and $N$ is the number of
options in $r$. To illustrate, the contribution of this function to
the score of a rule would be $0.26$ ($=(10181+3049)/(2*25699)$) for a
rule with options \CodeIn{prce} and \CodeIn{flowbits} and $0.01$
($=(155+108)/(2*25699)$) for a rule with options \CodeIn{itype} and
\CodeIn{icode}.

@@

\subsubsection{Number of content options.} We observed
that \percContentOptions\ of the rules from the ruleset we analyzed
contain content options, but the distribution of those contents per
rule is not uniform. Figure~\ref{fig:distribution-contents} shows the
distribution of number of contents in a rule. Results indicate nearly
73\% of the rules from our ruleset contain one to three content
options. Hence, we found that that information could help
\tname\ discriminate useful rules. \tname{} computes the contribution
of the number of content options to the score of a rule $r$ with the
fraction
$\frac{\mathit{rules\_per\_number\_of\_contents[len(r)]}}{\mathit{max(rules\_per\_number\_of\_contents)}}$,
where $\mathit{len(r)}$ denotes the number of content options in $r$
and $\mathit{rules\_per\_number\_of\_contents}$ denotes the
distribution of number of contents (encoded with a dictionary as in
the function described on
Section~\ref{sec:popularity-options}). Consequently the term
$\mathit{rules\_per\_number\_of\_contents[len(r)]}$ corresponds to the
number of rules in the ruleset with the same number of contents as
$r$. The denominator of the fraction normalizes the contribution in
the 0-1 range. To illustrate, the contribution of this heuristic
function to the score a rule would be $.64$ $(=5841/9164)$ to a rule
with 3 content options and $.18$ $(=1622/9164)$ to a rule with 5
content options.

@@

\subsubsection{Popularity of content strings.} 
This heuristic leverages content rarity to discriminate rules---it
weighs higher (respectively, lower) rules that use popular
(respectively, unpopular) strings in content options. The score of a
rule $r$ on this function is given by the arithmetic mean of the
popularity scores of each string used in contents in $r$. More
precisely, the contribution of content rarity is given by the
following formula:

{\small
\vspace{-1.5ex}
\[\sum_{i=1}^{N}\frac{\mathit{content\_frequency[content_i]}}{\mathit{max(content\_frequency)}}/N\]
\vspace{-0.5ex}
}
\noindent
where $\mathit{content_i}$ denotes the $i$th content in a given
rule, the term $\mathit{content\_frequency[\mathit{content_i}]}$
denotes the frequency of the string used in the $i$th content, the
term $\mathit{max(content\_frequency)}$ denotes the maximum frequency
observed across all strings appearing as content parameters, and $N$
is the number of content options in a given
rule. Figure~\ref{fig:distribution-strings} shows the distribution of
the ten most popular strings in our ruleset. To illustrate, let us
consider a rule with whose content options use the strings ``GET'' and
``ID'', respectively. The contribution of that rule for the
computation of similarity score would be 0.601 (=(1+.203)/2). The
relatively high weight reflects the fact that ``GET'' and ``ID'' are
popular content strings.

\subsubsection{\label{sec:popularity-content-modifiers}Popularity of http content modifiers.} As previously
mentioned, \percRulesWithContent\ of \suri\ rules involve content
options. Furthermore, nearly half of the rules that use content
options use content modifiers to qualify the search. Http modifiers
typically serve to specify parts of the message payloads that the
input string should be matched against. For example, the modifier
\CodeIn{http\_header} in the option \CodeIn{content: ``keep-alive'';
  http\_header} indicates that the string ``keep-alive'' should be
present in the header of the http message\footnote{A keep-alive
  connection attribute indicates that a single tcp connection should
  remain open for multiple http requests/responses.}. Note that, in
this case, the content modifier refers to a field of an http message,
which appears in the payload of a tcp message, which is the target of
the option \CodeIn{content}. Figure~\ref{fig:http-header-example}
illustrates possible content options used to match against certain
strings that appear in an http message. A check mark (respectively,
cross) indicates a match (respectively, no match).

@@

\tname\ builds on the observation that the strings commonly accessed
at positions associated with content modifiers (\eg{}, host,
connection) are more common. For example, historical data indicates
that content options that use the modifier \CodeIn{connection} are
much less likely than content options that use the modifier
\CodeIn{uri}. Figure~\ref{fig:distribution-content_modifiers} shows
the histogram of content modifiers for http. (We removed the prefix
\CodeIn{http} on the modifier for space.) Although content modifiers
are applicable to rules of any protocol supported by Suricata,
currently, \tname\ only supports this features for tcp and http; these
rules comprise $\sim$80\% of the rules of our data set. We compute the
heuristic function for content modifiers with the following formula:

\[\frac{\sum_{i=1}^{N}g(i)}{N},~g(i)=\frac{\sum_{j=1}^{M_i}\frac{\mathit{modifier\_frequency[modifier_{ij}}]}{\mathit{max(modifier\_frequency)}}}{M_i}\]

\noindent
where $g(i)$ is the contribution of content option $i$ to the score,
$N$ is the number of contents options present in a rule,
$\mathit{modifier\_frequency[modifier_{ij}}]$ denotes the popularity
of a modifier $j$ to content option $i$,
$\mathit{max(modifier\_frequency)}$ refers to the modifier with
maximum popularity (for normalization), and $M_i$ is the number of
content modifiers that could access the string associated with content
$i$.

To illustrate, consider a rule containing the option
\CodeIn{content:``/HtmlAdaptor''} (see Section~\ref{sec:jboss}). The
contribution of this option---\ie{}, the value of $\mathit{g(i)}$---to
the score of the rule is $0.5$ (=$\frac{10,111+11}{10,111*2}$). The
value of $M_i$, in this case, is 2 as the string ``/HtmlAdaptor''
could be accessed through the modifiers \CodeIn{uri} and
\CodeIn{request\_line}. The reason is that \tname\ identifies that
that string appears in the field \CodeIn{Request URI} (of an http
message from the malicious traffic) and that field is accessible
through these two modifiers. The relatively high heuristic value
reflects the fact that the string could be accessed by two popular
content modifiers.  As another example, consider the option
\CodeIn{content: ``keep-alive''}. In this case, either the modifier
\CodeIn{header} or the modifier \CodeIn{connection} could be used to
locate the string ``keep-alive'', stored in the field
\CodeIn{Connection} from an http message (see
Figure~\ref{fig:http-header-example}). Consequently the contribution
of this heuristic function to the corresponding rule would be $0.2$
(=$\frac{4089+29}{10111*2}$), in this case. Assuming that a rule uses
the two content options mentioned above, the aggregated contribution
of this heuristic function to the rule would be 0.35 (=(0.2+0.5)/2).

\subsubsection{Weight Optimization}
\label{sec:weight-optimization}
We optimized the weights of these heuristic functions as follows. We
ran \tname{} using different combinations of weights on a sample of
attacks and chose the combination that offered the best overall
performance, which we computed with the sum of the rankings of the
golden rule on each attack. The weight combination that led to the
smaller sum of positions (of the golden rule) in the rankings was
considered the best choice. We considered \emph{all} combinations of
the following weights 0, 0.25, 0.5, 0.75, and 1. Given that we have
four different functions and five possible weight values, we needed to
run \tname{} on the sample of attacks for 625 (=$5^4$) times. In the
end of the process, the weight combination
$\langle{}1,0.25,0.25,1\rangle$ was the best choice we found. Although
results showed that this strategy results in good performance, we
remain to evaluate other optimization strategies to find better
weights.

@@

\noindent
\textbf{Alternative methods for rule synthesis.} We discuss in the
following techniques similar in goal to ours. Unfortunately, we could
not access the tools implementing the techniques for side
comparison. Nevertheless, we found that there are important
differences between our work and related work. Vollmer
\etal{}~\cite{vollmer-etal-cics2011} propose the use of search to
derive rules for Snort, which are very similar to \suri's.  \Fix{Their
approach focuses on icmp attacks.} \Gui{The dataset used by them consists of manually produced ICMP packets using packet creation tools.}. It models every field of the icmp
packet in the chromosome of candidate solutions (\ie{}, a rule) of a
genetic search. The initial population is a set of candidate solutions
that randomly combine options, modelling the packet fields. They show
that they were able to generate rules without false negatives and only
3 false positives across 33K benign packets. The key differences
between our work and Vollmer~\etal{}'s are 1) the support of different
protocols and 2) the use of ranking to discriminate alternative
plausible rules. As for 1, our approach supports a variety of
protocols and options that refer to message payloads which
significantly increase the search space. The icmp rules they generate only
refer to message fields (see Section~\ref{sec:rules-and-packets}).
\MyComment{\Luc{eh possivel incluir contents em regras icmp tb. o q a secao 2.3 
diz q \textbf{geralmente} as regras nao-http possuem apenas field options}. }
As for 2, our solution additionally ranks plausible options, which
contain \emph{no} false positives or negatives with respect to the
benign and mallicious traffic considered.\Gui{Guruprasad \cite{guruprasad} also proposes an evolutionary framework, creating their own ICMP dataset as Vollmer, but also using DARPA 1999 \cite{darpa1999} and ISCX 2012 \cite{iscx} datasets for non-ICMP attacks. The produced rules reported a detection rate up to 96\%. Although Guruprasad supports more protocols than Vollmer, our approach still supports more options and protocols, making both key differences considered when comparing with Vollmer also relevant with Guruprasad.} Muthuregunathan
\etal{}~\cite{muthuregunathan-etal2009} propose a clustering method to
create rules. They characterize candidate solutions as a set of field
values and use a clustering algorithm---hybrid k-means partitioned
around menoids---to isolate malicious from benign
traffic. Subsequently, they optimize the formed clusters using genetic
algorithms and hill-climbing search. Ou approach differs from theirs
in the method used, results, and support for content
options. Kao~\etal~\cite{Kao2015AutomaticNR} proposed ARGS, a system
to synthesize http rules that take malicious traffic as input. ARGS
looks for a common pattern across the different inputs to define
rules. It does not take existing rules as input or benign
traffic. Consequently, false positive can be produced and need to be
handled manually by users. Our approach, in contrast, does not
generate false positives w.r.t. the input traffic.

@@

\noindent
\textbf{Rule repair.}~Hallahan~\etal{}~\cite{8102263} propose to
repair firewall rules based on false positive detected by the
rules. Although firewall and \nids\ rules have differences and the
problem addressed is different---repair not synthesis---the work is
similar in spirit and inspiring. We remain to evaluate how \tname\ can
be used for repair.

>>>>

\tname{} uses a composition of heuristic functions to rank the rules
produced in the previous step. Each of these functions uses a
different criterion to estimate how similar a new rule is to the rules
from public rulesets (\eg{},~\cite{emerging-threats-open}). The
intuition is that rules that look more similar to existing trusted
rules are more likely to reflect user's intention and be more
useful. The aggregated score of a rule is the weighted average across
the values produced by each heuristic function. The co-domain of each
function ranges on the 0-1 interval. Hence, the score of a rule also
ranges on the 0-1 interval. We describe in the following each of these
heuristic functions.

@@

\subsubsection{\label{sec:popularity-options}Popularity of options.}

\tname{} use the popularity of the options used in trusted rules as a
heuristic function---rules containing popular options score higher
compared to those containing unpopular
rules. Figure~\ref{fig:distribution-options} shows the histogram of
rule options for the ruleset we used~\cite{emerging-threats-open}. The
x-axis shows the options used in rules (the 10 most common) and the
y-axis shows the number of rules using the corresponding option. Note
that the options \CodeIn{content}, \CodeIn{flow}, and \CodeIn{prce}
are very popular. \tname\ uses the following formula to compute the
contribution of option popularity to the score of a rule $r$:
\indent
$\sum_{i=1}^{N}\frac{\mathit{option\_frequency[option_i]}}{\mathit{max(option\_frequency)}}/N$.

%% {\small
%% \vspace{-2ex}
%% \[

%% \]
%% \vspace{-2ex}
%% }

\noindent
The term $\mathit{option_i}$ denotes the $i$th option in the bitvector
encoding $r$. The term $\mathit{option\_frequency}$ encodes the
distribution of option popularity as a dictionary mapping numbers,
indicating popularity, to corresponding options. The expression
$\mathit{option\_frequency[option_i]}$ denotes the number of rules,
from our dataset, containing $\mathit{option\_i}$. The expression
$\mathit{max(option\_frequency)}$ refers to the maximum number of
rules for any dictionary entry (to normalize the measurement in the
0-1 range), and $N$ is the number of options in $r$. To illustrate,
the contribution of this function to the score of a rule would be
$0.26=$($10181$+$3049)/(2$*$25699)$ for a rule with options
\CodeIn{prce} and \CodeIn{flowbits} and
$0.01$=$(155$+$108)/(2$*$25699)$ for a rule with options
\CodeIn{itype} and \CodeIn{icode}.

@@

\subsubsection{Number of content options.} We observed
that \percContentOptions\ of the rules from the ruleset we analyzed
contain content options, but the distribution of those contents per
rule is not uniform. Figure~\ref{fig:distribution-contents} shows the
distribution of number of contents in a rule. Results indicate that
nearly 73\% of the rules from our ruleset contain one to three content
options. Hence, we found that that information could help
\tname\ discriminate useful rules. \tname{} computes the contribution
of the number of content options to the score of a rule $r$ with the
fraction
$\frac{\mathit{rules\_per\_number\_of\_contents[len(r)]}}{\mathit{max(rules\_per\_number\_of\_contents)}}$,
where $\mathit{len(r)}$ denotes the number of content options in $r$
and $\mathit{rules\_per\_number\_of\_contents}$ is the distribution of
number of contents. The expression in the numerator
%$\mathit{rules\_per\_number\_of\_contents[len(r)]}$
calculates the number of rules in the ruleset with the same number of
contents as $r$ whereas the denominator normalizes the value in the
0-1 range. To illustrate, the contribution of this function would be
$.64$~($=5841/9164$) and $.18$~($=1622/9164$) to the score of rules
with 3 and 5 options, respectively.

@@

%% {\small
%% \vspace{-1.5ex}
%% \[
%% \]
%% \vspace{-0.5ex}
%% }

\subsubsection{Popularity of content strings.} 
This heuristic leverages content rarity to discriminate rules. It
weighs higher (respectively, lower) rules that use popular
(respectively, unpopular) strings in content options. The score of a
rule $r$ on this function is the arithmetic mean of the popularity
scores of each string used in contents in $r$. More precisely, content
rarity is obtained with the following formula:
\indent
$\sum_{i=1}^{N}\frac{\mathit{content\_frequency[content_i]}}{\mathit{max(content\_frequency)}}/N$

\noindent
, where $\mathit{content_i}$ denotes the $i$th content in a given
rule, the term $\mathit{content\_frequency[\mathit{content_i}]}$
denotes the frequency of the string used in the $i$th content, the
term $\mathit{max(content\_frequency)}$ denotes the maximum frequency
observed across all strings appearing as content parameters, and $N$
is the number of content options in a given
rule. Figure~\ref{fig:distribution-strings} shows the distribution of
the ten most popular strings in our ruleset. To illustrate, consider a
rule whose content options use the strings ``GET'' and ``ID''. The
contribution of that rule for the computation of similarity score
would be $0.601$ $(=(1$+$.203)$/$2)$. The relatively high weight
reflects the fact that ``GET'' and ``ID'' are popular content strings.

@@

\subsubsection{\label{sec:popularity-content-modifiers}Popularity of http content modifiers.} As previously
mentioned, \percRulesWithContent\ of \suri\ rules involve content
options. Furthermore, nearly half of the rules that use content
options use content modifiers to qualify the search. Http modifiers
typically serve to specify parts of the message payloads that the
input string should be matched against. For example, the modifier
\CodeIn{http\_header} in the option \CodeIn{content: ``keep-alive'';
  http\_header} indicates that the string ``keep-alive'' should be
present in the header of the http message. (A keep-alive connection
attribute indicates that a single tcp connection should remain open
for multiple http requests/responses.) In this case, the content
modifier refers to an http field that appears in the payload of a tcp
message, which is the target of the option
\CodeIn{content}. Figure~\ref{fig:http-header-example} illustrates
possible content options used to match against certain strings that
appear in an http message. A check mark (respectively, cross)
indicates a match (respectively, no match).
\tname\ builds on the observation that the strings commonly accessed
at positions associated with content modifiers (\eg{}, host,
connection) are more common. For example, historical data indicates
that content options that use the modifier \CodeIn{connection} are
much less likely than content options that use the modifier
\CodeIn{uri}. Figure~\ref{fig:distribution-content_modifiers} shows
the histogram of content modifiers for http. (We removed the prefix
\CodeIn{http} on the modifier for space.) Although content modifiers
are applicable to rules of any protocol supported by Suricata,
currently, \tname\ only supports this features for tcp and http; these
rules comprise $\sim$80\% of the rules of our data set. We compute the
heuristic function for content modifiers with the following formula:

\indent
$\sum_{i=1}^{N}g(i)/N,~g(i)$=$\sum_{j=1}^{M_i}\frac{\mathit{modifier\_frequency[modifier_{ij}}]}{\mathit{max(modifier\_frequency)}}/M_i$

\noindent
, where $g(i)$ is the contribution of content option $i$ to the score,
$N$ is the number of contents options present in a rule,
$\mathit{modifier\_frequency[modifier_{ij}}]$ denotes the popularity
of a modifier $j$ to content option $i$,
$\mathit{max(modifier\_frequency)}$ refers to the modifier with
maximum popularity (for normalization), and $M_i$ is the number of
content modifiers that could access the string associated with content
$i$.
To illustrate, consider a rule containing the option
\CodeIn{content:``/HtmlAdaptor''} (see Section~\ref{sec:jboss}). The
contribution of this option (\ie{}, the value of $\mathit{g(i)}$) to
the score of the rule is $0.5$ (=$\frac{10,111+11}{10,111*2}$). The
value of $M_i$, in this case, is 2 as the string ``/HtmlAdaptor''
could be accessed through the modifiers \CodeIn{uri} and
\CodeIn{request\_line}. The reason is that \tname\ identifies that
that string appears in the field \CodeIn{Request URI} (of an http
message from the malicious traffic) and that field is accessible
through these two modifiers. The relatively high heuristic value
reflects the fact that the string could be accessed by two popular
content modifiers.

%%%%%%%%%%%%%%
%% Removed for space
%%%%%%%%%%%%%%

%% As another example, consider the option
%% \CodeIn{content: ``keep-alive''}. In this case, either the modifier
%% \CodeIn{header} or the modifier \CodeIn{connection} could be used to
%% locate the string ``keep-alive'', stored in the field
%% \CodeIn{Connection} from an http message (see
%% Figure~\ref{fig:http-header-example}). Consequently the contribution
%% of this heuristic function to the corresponding rule would be $0.2$
%% (=$\frac{4089+29}{10111*2}$), in this case. Assuming that a rule uses
%% the two content options mentioned above, the aggregated contribution
%% of this heuristic function to the rule would be 0.35 (=(0.2+0.5)/2).

\subsubsection{Weight Optimization}
\label{sec:weight-optimization}
We optimized the weights of these heuristic functions as follows. We
ran \tname{} using different combinations of weights on a sample of
attacks and chose the combination that offered the best overall
performance, which we computed with the sum of the rankings of the
golden rule on each attack. The weight combination that led to the
smaller sum of rankings was considered the best choice. We considered
\emph{all} combinations of the following weights 0, 0.25, 0.5, 0.75,
and 1. Given that there are four different functions and five possible
weight values, we needed to run \tname{} on the sample of attacks for
625 (=$5^4$) times. In the end of the process, the weight combination
$\langle{}1,0.25,0.25,1\rangle$ was the best choice we found. Although
results showed that this strategy results in good performance, we
remain to evaluate other optimization strategies to find better
weights.

@@

\noindent
\textbf{Alternative methods for rule synthesis.} We discuss in the
following techniques similar in goal to ours. Unfortunately, we could
not access the tools implementing the techniques for side
comparison. Nevertheless, we found that there are important
differences between our work and related work. Vollmer
\etal{}~\cite{vollmer-etal-cics2011} propose the use of search to
derive rules for Snort, which are very similar to \suri's.  \Fix{Their
approach focuses on icmp attacks.} \Gui{The dataset used by them consists of manually produced ICMP packets using packet creation tools.}. It models every field of the icmp
packet in the chromosome of candidate solutions (\ie{}, a rule) of a
genetic search. The initial population is a set of candidate solutions
that randomly combine options, modelling the packet fields. They show
that they were able to generate rules without false negatives and only
3 false positives across 33K benign packets. The key differences
between our work and Vollmer~\etal{}'s are 1) the support of different
protocols and 2) the use of ranking to discriminate alternative
plausible rules. As for 1, our approach supports a variety of
protocols and options that refer to message payloads which
significantly increase the search space. The icmp rules they generate only
refer to message fields (see Section~\ref{sec:rules-and-packets}).
\MyComment{\Luc{eh possivel incluir contents em regras icmp tb. o q a secao 2.3 
diz q \textbf{geralmente} as regras nao-http possuem apenas field options}. }
As for 2, our solution additionally ranks plausible options, which
contain \emph{no} false positives or negatives with respect to the
benign and mallicious traffic considered.\Gui{Guruprasad \cite{guruprasad} also proposes an evolutionary framework, creating their own ICMP dataset as Vollmer, but also using DARPA 1999 \cite{darpa1999} and ISCX 2012 \cite{iscx} datasets for non-ICMP attacks. The produced rules reported a detection rate up to 96\%. Although Guruprasad supports more protocols than Vollmer, our approach still supports more options and protocols, making both key differences considered when comparing with Vollmer also relevant with Guruprasad.} Muthuregunathan
\etal{}~\cite{muthuregunathan-etal2009} propose a clustering method to
create rules. They characterize candidate solutions as a set of field
values and use a clustering algorithm---hybrid k-means partitioned
around menoids---to isolate malicious from benign
traffic. Subsequently, they optimize the formed clusters using genetic
algorithms and hill-climbing search. Ou approach differs from theirs
in the method used, results, and support for content
options. Kao~\etal~\cite{Kao2015AutomaticNR} proposed ARGS, a system
to synthesize http rules that take malicious traffic as input. ARGS
looks for a common pattern across the different inputs to define
rules. It does not take existing rules as input or benign
traffic. Consequently, false positive can be produced and need to be
handled manually by users. Our approach, in contrast, does not
generate false positives w.r.t. the input traffic. \Gui{Fallahi and colleagues proposes a flow-based solution for automated rule generation. Instead of analyzing the packets individually, their algorithm investigates and creates the rules for flows in the network. The algorithm was tested using the ISCX 2012 dataset and showed good results in terms of precision, but it is limited to the type of attack. As it won't analyse individual details of each packet, it wouldn't be able to identify and generate rules for attacks that require detailed options, such as the HTTP PESC, RCE and LFI. https://ieeexplore.ieee.org/abstract/document/7585840}

@@

\noindent
\textbf{Rule repair.}~Hallahan~\etal{}~\cite{8102263} propose to
repair firewall rules based on false positive detected by the
rules. Although firewall and \nids\ rules have differences and the
problem addressed is different---repair not synthesis---the work is
similar in spirit and inspiring. We remain to evaluate how \tname\ can
be used for repair. \Gui{Ganesan and colleagues introduces an idea of generating new sets of rules based on modifications of existing rules. They used the community edition of snort rules from 2012 for the modifications and tested with the the pcap file from the MACCDC 2012 dataset. It was reported an increase in the number of alerts, but it wasn't analysed the false alarmrates for abduced rules. Their technique is parallel to the rule creation strategies, as the objective of the modified rules is to capture false positives, not new attacks. https://arxiv.org/abs/1903.12101 \Fix{I'm not sure if we can consider it 'rule repair', but I don't know where to put it.}}
